---
title       : Developing Data Products Project
subtitle    : Calculating MPG per MTCARS data
author      : S. Naficy
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---




## Miles Per Galon Application

The Miles Per Galon application uses the predict function in R to estimate a car miles per galon per the given parameters:
- Weigth
- Transmission Type
- Quarter mile time per Second

---

## The Data
The application uses the data that was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r}
mtcars

```

---

## The Prediction Model 
the following code is used to create the Model used in the predict function

```{r,results='hide'}
data(mtcars)
init_fit <- lm(mpg ~ ., data = mtcars)
best_fit <- step(init_fit, direction = "both")


```



The best_fit model shows that mpg is a function of Weigth(wt), Transmission Type(am), and Quarter mile time per Second(qsec)





---

## The Application URL

https://snaficy.shinyapps.io/ShinyApp/














